%% KT: June 9, 2020
\documentclass{aastex63} 
\usepackage{amssymb,amsmath}
\usepackage{url}
\usepackage{hyperref}

%%%%%%%%%%%%%%%%%%%%%%
\received{\today}
\revised{Feb 30, 2022}
\accepted{Feb 31, 2022}
\submitjournal{AJ}
\shorttitle{SDSS Stripe 82 Standard Stars Catalog: New and Improved}
\shortauthors{Thanjavur et al.}
\graphicspath{{./}{figures/}}

% user defined
\newcommand{\tbd}[1]{\textcolor{magenta}{#1}} % indicate TBDs
\def\eq#1{\begin{equation} #1 \end{equation}}
\def\mic              {\hbox{$\mu\mathrm{m}$}}
% paper 1
\def\pO               {\hbox{I007}}
\def\pOc               {\hbox{I007 catalog}}

\begin{document}
\title{Photometric Cross-Calibration and Comparison of the SDSS Stripe 82 Standard Stars Catalog with Gaia DR2, Pan-STARRS1, DES and CFIS Catalogs}

\correspondingauthor{Karun Thanjavur}
\email{karun@uvic.ca}

\author[0000-0003-1187-2544]{Karun Thanjavur}
\affiliation{Department of Physics \& Astronomy, University of Victoria, 3800 Finnerty Road, Victoria, BC V8P 5C2, Canada}

\author[0000-0001-5250-2633]{\v{Z}eljko Ivezi\'{c}}
\affiliation{Department of Astronomy and the DiRAC Institute, University of Washington, 3910 15th Avenue NE, Seattle, WA 98195, USA}

\author[0000-0002-7069-7857]{Sahar S. Allam}
\affiliation{Fermi National Accelerator Laboratory, Batavia, Il 60510, USA}

\author[0000-0001-7211-5729]{Douglas L. Tucker}
\affiliation{Fermi National Accelerator Laboratory, Batavia, Il 60510, USA}

\author[0000-0002-6261-4601]{J. Allyn Smith}
\affiliation{Dept. of Physics, Engineering \& Astronomy, Austin Peay State University, 601 College St., Clarksville, TN 37044, USA}
  
%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% Mark off the abstract in the ``abstract'' environment. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We extend the SDSS Stripe 82 Standard Stars Catalog reported in \citet{Ivez07} with
post-2007 SDSS imaging data. Our catalog lists averaged SDSS $ugriz$ photometry
for nearly a million stars brighter than $r\sim22$ matched with the earlier version of the catalog. 
However, this new version is based on 2-3 times more measurements per star, resulting in 1.4-1.7 
times smaller random errors than in the original catalog, and about three times smaller than those 
for individual SDSS runs. Random errors in the new catalog are below 0.01 mag for stars brighter 
than 20.0, 21.0, 21.0, 20.5, and 19.0 in $ugriz$, respectively. We achieve this error threshold by 
using Gaia DR2 Gmag photometry to derive gray photometric zeropoint corrections, as functions 
of R.A. and Declination, for the SDSS catalog, and Gaia's BP-RP colors to derive corrections in the 
$ugiz$ bands, relative to the $r$ band. We test the quality of recalibrated SDSS photometry by 
comparing it to Pan-STARRS1, DES and CFIS photometry for the same stars. This multi-survey 
comparison indicates that the spatial variation of photometric zero points in the updated SDSS 
catalog is well below 0.01 mag (rms), with typical values of 3-7 millimag in the R.A. direction and 
1-2 millimag in the Declination direction, except for the $u$ band with a scatter of about 6 millimag.
By comparing updated SDSS photometry with synthetic SDSS photometry for three white dwarfs
with the HST CalSpec absolute photometry data, we found statistically significant ($>3\sigma$) 
AB zeropoint offsets in the $riz$ bands, ranging from 0.015 mag to 0.035 mag, while in the $u$ 
and $g$ bands we only placed upper limits (at $2\sigma$: 0.038 mag and 0.028 mag, respectively).  
We also report a few minor photometric problems with all the surveys considered here, including 
Gaia DR2. Due to its large size and cross-checks with other surveys, this updated SDSS catalog can 
be used to robustly calibrate or test $ugriz$ photometry below 1\% level, for example, as needed 
for the commissioning phase of the Rubin Observatory Legacy Survey of Space and Time. 
\end{abstract}

%% Keywords from 2007 ZI
\keywords{catalogs -- instrumentation: photometers -- methods: data analysis -- standards -- surveys --
techniques: photometric}


\section{Introduction} \label{sec:intro}

\input{introduction}

\section{Datasets} \label{sec:data}

\subsection{SDSS Stripe 82 Imaging Data} \label{ssec:s82}

In the SDSS survey, Stripe 82 is a contiguous, 300 deg$^2$ equatorial region, which stretches between $-60^{\circ}\;\leq\;RA\;\leq\;60^{\circ}$ [20h to 4h], and $-1.266^{\circ}\;\leq\;Dec\;\leq\;1.266^{\circ}$. Following the initial concerted effort by the SDSS collaboration between 2001 and 2008 to map this region repeatedly to a forecast imaging depth, $r \leq 22$, several other surveys in various wavebands too have targeted this same patch of sky to provide a rich multi-wavelength dataset suitable for a variety of investigations. SDSS observations too have continued in this region \citep[e.g., the SDSS-II search for supernovae,][]{2008AJ....135..338F},
resulting in an imaging depth deeper than what was initially planned.  

Data from the SDSS imaging camera \citep{1998AJ....116.3040G} are collected in drift-scan mode. The images that correspond to the same sky location in each of the five photometric bandpasses (these five images are collected over $\sim$5 minutes, with an exposure time of 54 seconds for each band) are grouped together for simultaneous processing as a field. A field is defined as a 36 seconds (1361 pixels)  stretch of drift-scanning data from a single column of CCDs (sometimes called a ‘‘scan line’’; for more details, see \pO\ and references therein). 

\subsubsection{The 2007 SDSS Standard Star Catalog}

The SDSS standard star catalog published by \pO\ (version 2.6) was constructed by averaging multiple SDSS photometric observations (at least four per band, with a median of 10) in the $ugriz$ system. The catalog includes 1.01 million non-variable unresolved objects. The measurements for individual sources have random photometric errors below 0.01 mag for stars brighter than 19.5, 20.5, 20.5, 20, and 18.5 in $ugriz$, respectively (about twice as good as for individual SDSS runs). Several independent tests of the internal consistency suggested that the spatial variation of photometric zero points is not larger than $\sim$0.01 mag (rms).  

\subsubsection{Post-2007 SDSS data \label{ssec:DR15}}

In this work, we have used the SDSS Data Release 15 (DR15) as available in April 2019 \citep{Blan17}. In DR15, the Stripe 82 region is covered by 118 {\it runs}, which include 32,292 fields, each with observations in the five   $ugriz$ SDSS filters. Using our programmatic query tool, we obtained the processed data for all these runs from the DR15 public database. In the database, the data are presented as individual FITS tables, named \verb photoObj_<run>_<camcol>_<field>.fits. From each fits table, we extracted photometric and astrometric quantities, time of observation, and several ancillary data for all the objects into a formatted, 107-column wide ascii master file for further processing.

The objects in each of these data files were then matched with the standard stars in the \pO\ catalog using their mean sky positions (R.A. and Declination) and a matching radius of 0.5 arcsec. For matching, only deblended objects ({\it nchild}=0), lying between rows $64 < objc\_rowc < 1424$ in each field, were selected to avoid poor photometry due to blending or lying close to edges of the CCD. From these matched objects, only those with photometric error $<$0.1 mag were selected to compute photometric zeropoint offsets between the \pO\ catalog and DR15. These offsets were obtained independently for all runs and fields, and in all five filters, and applied to bring our DR15 based catalog to the same photometric scale as the \pO\ catalog -- in essence, we have re-calibrated photometry for all Stripe 82 runs in DR15 using the \pO\ catalog. In addition, the MJD and fractional MJD of observation were computed using the median of the TAI values (the GPS based time reported by the SDSS Apache Point Observatory) for these matched objects. In the final step, the photometric, astrometric and other details for each of these matched standard stars were written to independent (one per star) light curve files. Further processing of these light curves is described in Section~\ref{sec:averaging}. 

All these processing steps were completed on a single quad-core desktop needing several days of processing. The final dataset, consisting of all the light curves in the five $ugriz$ filters for the 1,006,849 standard stars in the \pO\ catalog resulted in $\sim$20 GB of tabular data. To make file search and access fast, the data have been chunked into sub-directories, each spanning 1 $\deg$ in RA, and 0.1 $\deg$ in Dec (a ``poor-man's'' two-dimensional tree structure). These light curve data files can be made available as a single tarball by emailing the contact author. 


\subsection{Gaia Data Release 2 (DR2) Data} \label{ssec:gaia}
 
The second Gaia Data Release, Gaia DR2, includes astrometry, photometry, radial velocities, and information on astrophysical parameters and variability, for sources brighter than magnitude Gmag$\sim$21 \citep{2018A&A...616A...1G}. This dataset
is based on the first 22 months of the mission and includes celestial positions and the apparent brightness in the broad-band G (Gmag hereafter) for approximately 1.7 billion sources. This data release also contains two additional broad-band magnitudes, the BP (330-680 nm) and RP (630-1050 nm), for 1.4 billion sources.
    
Gaia DR2 photometry is superior to ground-based photometry for sources with sufficient signal-to-noise ratio, and we use 
it to derive zeropoint corrections for SDSS photometry, as described in Section~\ref{sec:v34}. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Deep Energy Survey (DES) Data} \label{ssec:des}

\tbd{DT/SA to fill in details}
 
Dark Energy Survey \citep{2016MNRAS.460.1270D}

Old text from Doug, probably a good start but needs editing: 

We use the Dark Energy Survey Data Release 1 (DES DR1; Abbott et al.\ 2018) public data set. DES DR1 object catalog consists $\sim$ 400 million objects covering 5000$deg^{2}$ of the southern Galactic cap in the five DES grizY filters. The 10$sigma$ depth in grizY is 24.33, 24.08, 23.44, 22.69, and 21.44 mag, and median point-spread function is 1.12, 0.96, 0.88, 0.84, and 0.90 FWHM in grizY respectively, with a photometric precision of $<$1\% in all bands. The quoted astrometric precision is 151 mas (for a full discussion about the astrometric solution and the accuracy see Abbott et al.\ 2018). We made use of the DES DR1 access through the NOAO Data Lab (http://datalab.noao.edu) via Table Access Protocol (TAP) service, and downloaded the overlapping area with S82. We selected stars via SPREAD\_MODEL and SPREADERR\_MODEL (in the i-bands; in particular EXTENDED\_COADD $\leq$1 as described in eq.~2 of Abbott et al.\ 2018), with WAVG\_MAG\_PSF in AB mag keeping all good data with IMAFLAGS\_ISO==0 (in the i-band).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Pan-STARRS (PS1) Data} \label{ssec:ps1}

\tbd{KT to fill in details}

Pan-STARRS \citep{2010SPIE.7733E..0EK}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Canada-France Imaging Survey (CFIS) Data} \label{ssec:cfis}

\tbd{Emails from SGwyn to fill in details, see email on 6/18/2020}

{\bf Citations}: 

Ibata et al (2017) 2017ApJ...848..128I (Note interesting comparison with sDSS DR13 u-band photometry on page 3) 
CFIS DR2 notes on Evernote from Gwyn

The Canada-France Imaging Survey (CFIS) is a large observing program being carried out at the Canada-France-Hawaii Telescope to map the northern sky in the $MegaCam$ $u$- and $r$-bands. With a broad range of science goals, including providing ground-based optical photometry to complement the $Euclid$ space mission, CFIS aims to cover 10000 deg$^2$ in the $u$-band to a depth of 24.4mag with an uncertainty less than 0.2 mag. The corresponding $r$-band coverage would be smaller, 5000 deg$^2$ to an expected depth of ?? mag. For our analysis, we were provided the $u$-band data from the CFIS data release, DR2 in January 2020, which overlaps the Stripe 82 footprint; there are no CFIS $r$-band observations available for that region (Gwyn, personal comm.).  It should also be noted that in this region, CFIS data are available only for Declination $>$ 0.45 degree.

The CFIS Stripe 82 catalog contains close to 965000 sources, of which 315000 matched within a match radius of 0''.5 with stars in our catalog. The astrometry over the complete CFIS survey region has been calibrated against $Gaia$ DR1, thus reducing positional uncertainties to $<$ 0''.034 (Ibata ea 2017). For the objects in the Stripe 82 region, we crosschecked the positions against matched objects in our $Gaia$ DR2 catalog (see \S \ref{ssec:gaia}) and found a median offset of 0''.033. From the matched objects, we select only bright stars, redder than the main sequence by applying cuts of 1. $\leq (u-g)_{SDSS} \leq 2.1$, and $r_{SDSS} \leq $ 20 mag, similar to the cuts used by Ibata (2017) in their photometric cross-calibration using SDSS DR13. This color-magnitude cut yields 150114 stars, which are used in the comparison described in \S \ref{sec:CFIStest}.   
  
%   MAG_AUTO vs MAG_COG: That's pretty standard. While MAG_AUTO works well for galaxies, but not stars. For fainter stars, it systematically underestimates the Kron-radius.

% - I'd be interested in seeing which transformation you derived. I use the one described on this page: \url{https://www.cadc-ccda.hia-iha.nrc-cnrc.gc.ca/en/megapipe/docs/filt.html}

% - The SDSS and CFIS filters are different enough that u_SDSS-u_CFIS should start to be thought of as a colour, rather than a shift in filter. Metalicity will have non-negliable effect. I'm not surprised at all that there is 0.03 scatter.

% - On the subject of metalicity, I would view any attempt use GAIA to predict u-magnitudes as quixotic. Dust will also cause problems.

% - My error analysis for the u-band zero-point derived from Pan-STARRS plus GAIA results in an RMS scatter of 0.02 mags in the zero-points. 0.03 (from your Dec plot) seems a little high. However that was measured over the whole survey, so it maybe that the STRIPE-82 part of CFIS is slightly worse than average.

% - Following from that last point, have you considered extending your analsis to the rest of the sky? I find the coloured, all-sky plots very revealing.

{\bf Zeljko 6/19/2020}

% - MAG_AUTO vs MAG_COG: That's pretty standard. While MAG_AUTO works well for galaxies, but not stars. For fainter stars, it systematically underestimates the Kron-radius.

% OK, I didn?t know that - it?s great that there is an explanation! 

% - I'd be interested in seeing which transformation you derived. I use the one described on this page:
% \url{https://www.cadc-ccda.hia-iha.nrc-cnrc.gc.ca/en/megapipe/docs/filt.html}

% We don?t use analytic transformations (too many band and color combinations with multiple surveys/catalogs). Given that we have ~1 million stars, we simply use binned medians, with  very narrow bins (a few hundredths of mag) and then use linear interpolation. Given that the color terms typically have small dynamic ranges and are fairly linear, this numerical approach works fine (the contribution of numerical noise to the final zeropoint scatter is well below 1 milimag). 

% For the SDSS vs. CFIS comparison, we tried to regress uSDSS-uCFIS vs. both g-i color and u-g color, with similar results. We adopted the u-g color for the final analysis, and only blue  stars. The attached plot shows individual stars as blue dots and the binned median as larger yellow dots. As you can see, the relationship is fairly linear across the entire color range, and certainly linear between the successive bins. 

% Should you wish so, we can easily make the SDSS-CFIS matched star catalog available to you.

% - The SDSS and CFIS filters are different enough that u_SDSS-u_CFIS should start to be thought of as a colour, rather than a shift in filter. Metalicity will have non-negliable effect. I'm not surprised at all that there is 0.03 scatter.

% Yes, exactly, we treat the delta(u) it as a color. But metallicity would play a role in our comparison only if there is a substantial metallicity variation across the analyzed region. We know from other work that the variations are small enough not to play a significant role. Thus, the impact of metallicity  on the uSDSS-uCFIS difference is calibrated out in our approach and the scatter in magnitude  difference is dominated by random errors (due to limited photon statistics, background noise and  plausibly readout noise), and by zero point errors, which are likely functions of both R.A. and Dec.  The fact that the scatter of 0.03 mag does not depend on color, magnitude nor position argues that  it?s due to random errors from either CFIS, SDSS or from both. But since the SDSS multi-epoch observations limit the SDSS contribution to <0.01 mag, the scatter of 0.03 mag must be dominated by CFIS.

% Now, you could easily prove me wrong if you have multiple epochs with CFIS u band data. You can simply compare two independent measurements and see what is the empirical rms scatter vs. magnitude.  


% - On the subject of metalicity, I would view any attempt use GAIA to predict u-magnitudes as quixotic. Dust will also cause problems.

% We consider the u-r vs. BP-RP color-color diagram and fit the stellar locus in that diagram empirically. This method is essentially the same approach as used for the so-called ?s? color in this paper
% \url{http://faculty.washington.edu/ivezic/Publications/AN2004.pdf}
% which we used to assess photometric zero point error in SDSS photometry.

% As you said, for a given value of BP-RP color the corresponding u-r color will also depend on metallicity and dust, but *as long as they don?t change much*, their effects will get absorbed into the empirical locus description. For relative measures, such as variation of the zero points with R.A. and Dec, it works without major systematics (partially because Stripe 82 never gets close to the Galactic plane and lots of dust, and the halo metallicity distribution is fairly smooth). 

% - My error analysis for the u-band zero-point derived from Pan-STARRS plus GAIA results in an RMS scatter of 0.02 mags in the zero-points. 0.03 (from your Dec plot) seems a little high. However that was measured over the whole survey, so it maybe that the STRIPE-82 part of CFIS is slightly worse than average.

% I am assuming here that you meant R.A. plot - not Dec plot - because discrepancies in Dec plot are due to SDSS problems! 

% It?s certainly possible that Stripe 82 is worse. How large were your pixels? Larger pixels will tend the smooth ZP error variation. Our pixels for RA variation are about 2 deg by 2.5 deg. 

% - Following from that last point, have you considered extending your analsis to the rest of the sky? I find the coloured, all-sky plots very revealing.

% It?d be great to do so, but our catalog extends only over Stripe 82 because that?s the only  region on the sky where SDSS obtained ~20 epochs. The main point of our catalog is to  average those multiple epochs to reduce random and systematic errors, with an extra step of correcting a posteriori for obvious zero point errors.

 
%  The data you requested is available here:

 %\url{https://www.cadc-ccda.hia-iha.nrc-cnrc.gc.ca/files/vault/sgwyn/stripe82/cfis_stripe82.dat}

% The last column is a indicator of star/galaxy separation, as discussed in the Evernote. Values between 0.9 and 1.1 are mostly like stars. Values below are mostly likely cosmic rays (Strip82 includes patches where we only have a single image) and values above are most likely galaxies. There is no r-band coverage.

% I've given you MAG_COG = Curve of Growth (again, documented in the Evernote) and MAG_AUTO = Kron-type magnitude.
        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{{\it GALEX} Data} \label{ssec:galex}

The Galaxy Evolution Explorer ($GALEX$) all-sky survey catalog in the NUV (1771-2831 \AA) and FUV (1344-1786 \AA) bands provides a unique photometric dataset to constrain the u-band of a multiband survey such as the SDSS. Processed and calibrated archival data from the eight year, All-sky Imaging (AIS) and Medium depth Imaging (MIS) surveys are available at $MAST$\footnote{\url{https://galex.stsci.edu/GR6/}}. Due to the failure of the FUV detector midway through the survey, the available imaging depth in this band is shallower by nearly 1 ABmag than the NUV depth of 20.8 ABmag in the AIS. Overall, the source number count in the FUV is, on average, only a tenth of that in the NUV. Given these limitations in the FUV survey, we extracted only sources in the NUV catalog corresponding to the Stripe 82 footprint.  
 
\citet{2017ApJS..230...24B} provide full details of the GALEX survey, and we summarize only the NUV details, which are pertinent to our analysis here. The survey area had a fairly uniform coverage, leading to total exposure times of $\sim$150s in the AIS, and $\sim$1500s in the MIS. The corresponding NUV survey depths are 20.8 and 22.7 ABmag in the two surveys respectively. Objects in the S82 region were extracted and matched with our SDSS catalog using a matching aperture radius of 3'', which corresponds to the matching radius used internally by GALEX to match their NUV and FUV sources. The GALEX catalogs do not list the RA, Dec positional errors for their sources, and we found their listed sky positions generally carry a greater uncertainty than the other catalogs used in this work.

Our matched GALEX catalog consists of 150945 NUV sources in the S82 footprint for which we obtained NUV aperture magnitudes and uncertainties, as well as various fitted geometric measures for each of them. The astrometry has greater uncertainty than that of SDSS, with mean positional uncertainties of ??''. We also find that the available depth in the S82 region is not very deep, with $>$80\% of the matched sample brighter than r=18 mag. {\bf Add a few more details, eg mean positional uncertainty, from the matched SDSS-Galex catalog}
  

%% From {\bf Doug's email on 10/22} To make the process simpler, we first transformed the GALEX NUV to an estimated u-band using the transformation equation we sent yesterday.  That gets things a lot closer than just starting directly from GALEX NUV.  The E(B-V) tweak has not yet been included; using some sort of median binning like was done to improve the $u_{est}$ to $u_{sdss}$ transformation may be in order.  The results look like they may be qualitatively similar in scope to the CFIS u-band comparison (but sometimes opposite in sign!)  The RA,DEC positions from GALEX seem a bit worse than some of the other catalogs; so we used a match radius of 3 arcsec instead of 1 arcsec in the python notebook (matching SDSS coordinates to GALEX coordinates).
 
%% The GALEX catalog in the Stripe82 area can be found here:
%% \url{https://data.darkenergysurvey.org/public_calib/SDSS_Stripe82_stuff/index.html}

%% It was originally matched to SDSS DR13 by Sahar a couple years ago.  The GALEX catalog is indeed from the Bianchi et al. (2017) \citep{2017ApJS..230...24B}.  As it turns out, it does not go very deep (c. 80\% of the sample is brighter than r=18.0) and  -- as alluded above ? the astrometry seems to be noticeably noisier than that of SDSS.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\section{The Construction and Analysis of the New v3.4 Catalog \label{sec:v34}}
%% \input{zeljko2.tex}
\input{zeljko2Galx.tex} % This contains a sec on Galex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions} \label{sec:disc}

To enable further progress in cosmological and other high-precision photometric measurements, 
modern multi-band photometric sky surveys aim to deliver measurements accurate at the 1\% 
(0.01 mag) level. Over the last decade a number of such large-scale surveys approached, and
often exceeded this photometric accuracy threshold. For ground-based surveys, that are 
affected by variable atmospheric effects and hardware responses to changes in local environment
(e.g. temperature), significant improvements can be achieved by averaging multiple observations. 

In this paper, we have described the construction and tests of an updated version of the so-called
SDSS Stripe 82 Standard Star catalog \citep{Ivez07} that lists averaged SDSS photometry for about
a million non-variable stars. Additional post-2007 SDSS data include about 
2-3 times more measurements per star than in the original catalog, resulting in 1.4-1.7 times smaller 
random photometric errors (precision) than in the original catalog, and about three times as small 
as for individual SDSS runs.

Thanks to the availability of photometric data from recent wide-field surveys (Gaia, DES, Pan-STARRS
and CFIS), we were able to derive robust zeropoint corrections and establish that this new catalog
is superior to the original catalog. Using a combination of comparison to other catalogs and 
astrophysical constraints, we find that that the contribution of the zeropoint errors to photometric
errors is $<5$ millimag for the $gri$ bands, and $<10$ millimag for the $u$ and $z$ bands. 

Various catalog cross-comparisons have revealed minor problems with all the analyzed catalogs.
For example, we detected DES $z$ band zeropoint errors of up to 0.01-0.02 mag, as a function 
of R.A., and demonstreted that Gaia Gmag magnitudes appear too faint by about 0.02 mag at
Gmag$\sim$20.
 
We constrained offsets from the absolute AB magnitude scale using three white dwarfs with the 
HST CalSpec absolute photometry data. In the $riz$ bands we measured significant ($>3\sigma$) 
deviations, ranging from 0.015 mag to 0.035 mag (see Table~\ref{tab:AB}), while in the $u$ and $g$ 
bands we only placed upper limits (at $2\sigma$: 0.038 mag and 0.028 mag, respectively).  

Thanks to its high stellar density, about 1 star per square arcmin, and demonstrated sub-percent 
photometry, this catalog is a good resource for both calibrating and testing other surveys. In
particular, it will enable high-precision photometric testing of data collected during the 
commissioning phase of the Rubin Observatory Legacy Survey of Space and Time. 
  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgments
Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating
Institutions, the National Science Foundation, the US Department of Energy, the National Aeronautics and 
Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education 
Funding Council for England. The SDSS Web site is http://www.sdss.org.
 
\vspace{5mm}
\facilities{SDSS, Pan-STARRS, DECam, CFHT}

\software{numpy \citep{numpy}, matplotlib \citep{matplotlib}, scipy \citep{scipy}, 
       astropy \citep{astropy-1, astropy-2}, astroML \citep{2012cidu.conf...47V}.}

%%%%%%%%%%%%%%%%%%%%%
%% BIBLIOGRAPHY
\bibliography{S82SSC}{}
\bibliographystyle{aasjournal}

%\appendix
%\section{Appendix information}
%
%Here is Appendix A.
 
\end{document}
 




name     &     R.A. (deg)    &      Dec (deg)       &     $V$   &     $B-V$   &   
  GD50  &    57.209108    &    $-$0.975636   &   14.06  &  $-$0.28   &  13.409  & 13.784 & 13.784 & 14.6545  & $-$9999  \\ 

                                                                                                 A$_r$ 
                                                                                          &  0.513    &  13.376  & 13.816 & 14.279 & 14.649 & 15.002  






GAP? 
lds749b   323.067638   0.254000 14.463  14.550  14.8037  15.0312  15.2784

